SummaryStats

### 2023-05-11 analysis/code/stacked_did/SubExperiments.Rmd
#16 go over existing subexps code

```{r data import}
build <- read_csv("analysis/input/build.csv") %>% 
  select(city_id, year, terr_id, final_full_year, 
        extinction, treatment, extinction_of, count_diff)

>>>>

```{r data import}
build <- read_csv("analysis/input/build.csv") %>% 
  select(city_id, year, terr_id, treatment, extinction_of, count_diff)
